### 2015-05-13 term-paper/paper.tex
[term-paper] layout

\documentclass[aps,twocolumn,secnumarabic,balancelastpage,amsmath,amssymb,nofootinbib]{revtex4}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{chapterbib}
\usepackage{color}
\usepackage{graphics}
\usepackage[pdftex]{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{epsf}
\usepackage{bm}
\usepackage{tikz}
\usepackage{asymptote}
\usepackage{thumbpdf}
\usepackage{bbm}
\usepackage{amscd}
\usepackage{units}
\usepackage{textcomp}
\usepackage[utf8x]{inputenc}
\usepackage{feyn}
\usepackage{feynmp}
\usepackage[colorlinks=true]{hyperref}
\newcommand{\drelectron}[1]{\node at #1 [circle, draw, inner sep=0pt, minimum size=1pt] {\_}}

\newcommand{\ud}{\mathrm{d}}
\newcommand{\ue}{\mathrm{e}}
\newcommand{\ui}{\mathrm{i}}
\newcommand{\res}{\mathrm{Res}}
\newcommand{\Tr}{\mathrm{Tr}}
\newcommand{\dsum}{\displaystyle\sum}
\newcommand{\dprod}{\displaystyle\prod}
\newcommand{\dlim}{\displaystyle\lim}
\newcommand{\dint}{\displaystyle\int}
\newcommand{\fsno}[1]{{\!\not\!{#1}}}
\newcommand{\eqar}[1]
{
  \begin{align*}
    #1
  \end{align*}
}
\newcommand{\eqarn}[1]
{
  \begin{align}
    #1
  \end{align}
}
\newcommand{\texp}[2]{\ensuremath{{#1}\times10^{#2}}}
\newcommand{\dexp}[2]{\ensuremath{{#1}\cdot10^{#2}}}
\newcommand{\eval}[2]{{\left.{#1}\right|_{#2}}}
\newcommand{\paren}[1]{{\left({#1}\right)}}
\newcommand{\lparen}[1]{{\left({#1}\right.}}
\newcommand{\rparen}[1]{{\left.{#1}\right)}}
\newcommand{\abs}[1]{{\left|{#1}\right|}}
\newcommand{\sqr}[1]{{\left[{#1}\right]}}
\newcommand{\crly}[1]{{\left\{{#1}\right\}}}
\newcommand{\angl}[1]{{\left\langle{#1}\right\rangle}}
\newcommand{\tpdiff}[4][{}]{{\paren{\frac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}}_{#4}}}
\newcommand{\tpsdiff}[4][{}]{{\paren{\frac{\partial^{#1}}{\partial {#3}{}^{#1}}{#2}}_{#4}}}
\newcommand{\pdiff}[3][{}]{{\frac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}}}
\newcommand{\diff}[3][{}]{{\frac{\ud^{#1} {#2}}{\ud {#3}{}^{#1}}}}
\newcommand{\psdiff}[3][{}]{{\frac{\partial^{#1}}{\partial {#3}{}^{#1}} {#2}}}
\newcommand{\sdiff}[3][{}]{{\frac{\ud^{#1}}{\ud {#3}{}^{#1}} {#2}}}
\newcommand{\tpddiff}[4][{}]{{\left(\dfrac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}\right)_{#4}}}
\newcommand{\tpsddiff}[4][{}]{{\paren{\dfrac{\partial^{#1}}{\partial {#3}{}^{#1}}{#2}}_{#4}}}
\newcommand{\pddiff}[3][{}]{{\dfrac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}}}
\newcommand{\ddiff}[3][{}]{{\dfrac{\ud^{#1} {#2}}{\ud {#3}{}^{#1}}}}
\newcommand{\psddiff}[3][{}]{{\frac{\partial^{#1}}{\partial{}^{#1} {#3}} {#2}}}
\newcommand{\sddiff}[3][{}]{{\frac{\ud^{#1}}{\ud {#3}{}^{#1}} {#2}}}

\begin{document}
\tikzstyle{every picture}+=[remember picture]
\title{Confinement induced resonance}
\author{Yichao Yu}
\email{yuyichao@mit.edu}
\homepage{http://yyc-arch.org/}
\date{\today}
\affiliation{Harvard Department of Physics}

\begin{abstract}
\end{abstract}

\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

\section{Feshbach Resonance}
\subsection{$T$-Matrix and scatter length}
\subsection{Multichannel scattering and Feshbach resonance}

\section{Confinement induced resonance}

\section{Conclusion}

\bibliography{paper}
\end{document}

### 2015-05-14 term-paper/paper.tex
[term-paper] scatch
[term-paper] abstract

@@
 \begin{abstract}
+  We present a formal derivation of the confinement induced resonance for particles in a lower dimension.
+The generic $T$-matrix method is used to calculate the $S$-wave collisional property between two ultra-code atoms.
+We show the breakdown of a naive approach to describe such low dimensional system near a Feshbach resonance and preform a real three dimensional calculation to include additional effect from the confinement.
+The normalization of the high energy states in such cases are done by comparing to the result in free space.
 \end{abstract}
@@
 \section{Introduction}
-
+In the field of ultra-cold atoms and molecules, the collisional properties between the particles play an important role both for cooling into quantum degeneracy and as a source of correlation and entanglement in a many-body system.
 \section{Feshbach Resonance}
 \subsection{$T$-Matrix and scatter length}
+
+% S Wave (L=0 isotropic)
+% k \rightarrow 0
+% r \rightarrow \infty
+\eqar{
+  \Psi\paren{\vec r}=&\ue^{\ui \vec k_0\cdot \vec r}-\Psi_{s}
+  \approx&\ue^{\ui \vec k_0\cdot \vec r}-\frac{a}{r}
+}
+
+% Schroedinger equation
+% E=\frac{k^2}{m}
+% U(\vec k, \vec k')=\int\ud^3\vec r\int\ud^3\vec r'U\paren{\vec r-\vec r'}\ue^{\ui\vec k\cdot\vec r}\ue^{-\ui\vec k'\cdot\vec r'}
+\eqar{
+  \frac1{m}\paren{k^2-k'^2}\Psi_{s}\paren{\vec k'}=&U\paren{\vec k', \vec k}+\int\frac{\ud^3 k''}{\paren{2\pi}^3}U\paren{\vec k', \vec k''}\Psi_s\paren{\vec k''}
+}
+
+Define $T$ matrix
+\eqar{
+  T\paren{\vec k', \vec k}=&U\paren{\vec k', \vec k}+\int\frac{\ud^3k''}{\paren{2\pi}^3}\frac{U\paren{\vec k', \vec k''}}{k^2/m-k''^2/m+\ui 0}T\paren{\vec k'', \vec k}\\
+  \Psi_s\paren{\vec k'}=&\frac{m}{k^2-k'^2+\ui 0}T\paren{\vec k', \vec k, \frac{k^2}{m}}\\
+  f\paren{\vec k', \vec k}=&-\frac{m}{4\pi\hbar^2}T\paren{\vec k', \vec k, \frac{k^2}{m}}
+}
+
+% Effective interaction
+% Energy cut-off \varepsilon_c
+% k_c, R
+\eqar{
+  \tilde U\paren{\vec k', \vec k}=&U\paren{\vec k', \vec k}+\int_{k''^2/m>\varepsilon_c}\frac{\ud^3 k''}{\paren{2\pi}^3}\frac{\tilde U\paren{\vec k', \vec k''}}{k^2/m-k''^2/m+\ui 0}\tilde U\paren{\vec k'', \vec k}
+}
+\eqar{
+  T\paren{\vec k', \vec k}=&\tilde U\paren{\vec k', \vec k}+\int_{k''^2/m<\varepsilon_c}\frac{\ud^3 k'}{\paren{2\pi}^3}\frac{\tilde U\paren{\vec k', \vec k''}}{k^2/m-k''^2/m+\ui0}T\paren{\vec k'', \vec k}
+}
+% U\paren{\vec r}=U_0\delta^3\paren{\vec r}
+% Energy conservation
+% mainly k' == k
+\eqar{
+  \frac{1}{f\paren{k}}=&-\frac{4\pi}{mU_0}+4\pi\int_{\abs{q}<1/R}\frac{\ud^3q}{\paren{2\pi}^3}\frac{1}{k^2-q^2+\ui0}\\
+  =&\frac{1}{2\pi^2}\paren{-\frac{1}{R}-\frac{k}{2}\ln\paren{-\frac{R^{-1}-k-\ui0}{R^{-1}+k+\ui0}}}\\
+  \approx&\frac{1}{2\pi^2}\paren{-\frac{1}{R}-\frac{\ui\pi k}{2}+k^2R}
+}
+
+% f\paren{0}=-a
+\eqar{
+  a=&\frac{\pi}{2}\frac{R}{1+\frac{2\pi^2R}{mU_0}}\\
+  f\paren{k}=&\frac{1}{a^{-1}+r_{eff}k^2/2-\ui k}
+}
+% Dependency of U_0 on R
+
 \subsection{Multichannel scattering and Feshbach resonance}
+% Hamiltonian
+\eqar{
+  \hat H_0|\vec k\rangle=&
+}
+% Solution
+
+% Bound states
+
+% Compare to generic fomula and get scattering length
 
 \section{Confinement induced resonance}
+% Seperate COM and relative
+
+% Cutoff
+
+% Compare to 3-d
+
+% Bound state
+
+% Scattering length
 

### 2015-05-14 term-paper/paper.tex
[term-paper] 2.1

@@
 \section{Introduction}
-In the field of ultra-cold atoms and molecules, the collisional properties between the particles play an important role both for cooling into quantum degeneracy and as a source of correlation and entanglement in a many-body system.
+In the field of ultra-cold atoms and molecules, the collisional properties between the particles play an important role for cooling into quantum degeneracy.
+The tunability of the scattering length using Feshbach resonance opens the door for engineering the interaction and using it as a source of correlation and entanglement in a many-body system.
+
 \section{Feshbach Resonance}
-\subsection{$T$-Matrix and scatter length}
+% Cite optical feshbach resonance
+Feshbach resonance is a way to tune the interaction between two atoms.
+It appears as a divergence in the scattering length when the energy of a molecular bound state matches or is closed to the energy of the free atom state.
+The relative energy between the molecular and atomic is usually tuned using the magnetic field and the difference in Zeeman effect between the two states although optical dressing has also been used on excited metastable state.\\
 
-% S Wave (L=0 isotropic)
-% k \rightarrow 0
-% r \rightarrow \infty
+In this section, we will describe a formal way to calculate the properties of $S$-wave scattering at low temperature.
+We will then apply this framework to a simplified model of Feshbach resonance consists of a open channel for the free atomic state and a closed channel for the molecular bound state.
+
+\subsection{Wave function of a scattering process}
+In a scattering problem, the wave function can be broken into the incident wave $\Psi_i$ and the scattered wave $\Psi_s$ where the incident wave is usually a plain wave
+\[\Psi_i=\ue^{\ui\vec k\cdot\vec r}\]
+and the scattered wave can be expressed as a spherical wave centered around the scattering core ($\vec r=0$)
+\[\Psi_s=\frac{f\paren{\theta}}{r}\ue^{\ui k'r}\]
+For all the discussion in this paper, we are taking the limit of low temperature (i.e.
+low kinetic energy) in which case the scattering is limitted to $S$-wave (angular momentum $L^2=0$) and in the limit of long wavelength $k\rightarrow0$.
+In such a limit, the total wave function can be written as
 \eqar{
-  \Psi\paren{\vec r}=&\ue^{\ui \vec k_0\cdot \vec r}-\Psi_{s}
+  \Psi\paren{\vec r}=&\Psi_i\paren{\vec r}+\Psi_s\paren{\vec r}\\
   \approx&\ue^{\ui \vec k_0\cdot \vec r}-\frac{a}{r}
 }
+where $a$, which describe the fraction being scattered, is defined as the scattering length.
+In order to solve this problem, it is convinient to express the Schr\"odinger equation in the momentum space
+\eqar{
+  \frac{k^2-k'^2}{m}\Psi_{s}\paren{\vec k'}=&U\paren{\vec k', \vec k}+\int\frac{\ud^3 k''}{\paren{2\pi}^3}U\paren{\vec k', \vec k''}\Psi_s\paren{\vec k''}
+}
+where $U\paren{\vec k', \vec k}$ is the Fourier transform of the interaction
+\[ U(\vec k', \vec k)=\int\ud^3\vec r\int\ud^3\vec r'U\paren{\vec r'-\vec r}\ue^{\ui\vec k'\cdot\vec r'}\ue^{-\ui\vec k\cdot\vec r}\]
+and we have used the fact that the interaction is short range and the energy of the state is determined by the long distance behavior of the incident state $E_k=k^2/2m$.
 
-% Schroedinger equation
-% E=\frac{k^2}{m}
-% U(\vec k, \vec k')=\int\ud^3\vec r\int\ud^3\vec r'U\paren{\vec r-\vec r'}\ue^{\ui\vec k\cdot\vec r}\ue^{-\ui\vec k'\cdot\vec r'}
-\eqar{
-  \frac1{m}\paren{k^2-k'^2}\Psi_{s}\paren{\vec k'}=&U\paren{\vec k', \vec k}+\int\frac{\ud^3 k''}{\paren{2\pi}^3}U\paren{\vec k', \vec k''}\Psi_s\paren{\vec k''}
-}
+\subsection{$T$-Matrix and effective interaction}
 
@@
   T\paren{\vec k', \vec k}=&U\paren{\vec k', \vec k}+\int\frac{\ud^3k''}{\paren{2\pi}^3}\frac{U\paren{\vec k', \vec k''}}{k^2/m-k''^2/m+\ui 0}T\paren{\vec k'', \vec k}\\
-  \Psi_s\paren{\vec k'}=&\frac{m}{k^2-k'^2+\ui 0}T\paren{\vec k', \vec k, \frac{k^2}{m}}\\
-  f\paren{\vec k', \vec k}=&-\frac{m}{4\pi\hbar^2}T\paren{\vec k', \vec k, \frac{k^2}{m}}
+  \Psi_s\paren{\vec k'}=&\frac{m}{k^2-k'^2+\ui 0}T\paren{\vec k', \vec k}\\
+  f\paren{\vec k', \vec k}=&-\frac{m}{4\pi\hbar^2}T\paren{\vec k', \vec k}
 }

### 2015-05-14 term-paper/paper.tex
[term-paper] 2.2

@@
 For all the discussion in this paper, we are taking the limit of low temperature (i.e.
-low kinetic energy) in which case the scattering is limitted to $S$-wave (angular momentum $L^2=0$) and in the limit of long wavelength $k\rightarrow0$.
+low kinetic energy) in which case the scattering is limitted to $S$-wave (angular momentum $L^2=0$).
+We also assume that the interaction is short range so that the behavior is regular for long wavelength and we can take the limit of $k\rightarrow0$.
 In such a limit, the total wave function can be written as
@@
 
-\subsection{$T$-Matrix and effective interaction}
+\subsection{$T$-Matrix}
+The $T$-matrix is defined as a map from the initial state of the scattering (which is a $\delta$ function in $k$ space in our case) to the final state. It is defined as
+\eqar{
+  T\paren{\vec k', \vec k}=&U\paren{\vec k', \vec k}+m\int\frac{\ud^3k''}{\paren{2\pi}^3}\frac{U\paren{\vec k', \vec k''}}{k^2-k''^2+\ui 0}T\paren{\vec k'', \vec k}}
+where the $+\ui 0$ denotes a infinitesimal quantity to ensure that we have outgoing waves.
+Note the similarity with the equation satisfied by the scattered wavefunction.
+Using the $T$-matrix, we can express the scattered wavefunction as
+\[\Psi_s\paren{\vec k'}=\frac{m}{k^2-k'^2+\ui 0}T\paren{\vec k', \vec k}\]
+And we cans also define the scattering amplitude as
+% \[f\paren{\vec k', \vec k}=-\frac{m}{4\pi\hbar^2}T\paren{\vec k', \vec k}\]
+\[f\paren{\vec k', \vec k}=-\frac{m}{4\pi}T\paren{\vec k', \vec k}\]
+For the problem we are considering, we will take the limit of $k, k'\rightarrow0$, therefore
+\[\Psi_s\paren{\vec k'}=\frac{m}{k^2-k'^2+\ui 0}T\paren{0, 0}\]
+In real space
+\eqar{
+  \Psi_s\paren{\vec r}=&\int\frac{\ud k'^3}{\paren{2\pi}^3}\frac{m\ue^{\ui\vec k'\cdot\vec r}}{k^2-k'^2+\ui 0}T\paren{0, 0}\\
+  =&-\frac{m\ue^{\ui kr}}{4\pi r}T\paren{0, 0}
+}
+and by comparing to the form of $\Psi_s$ at low temperature we have $f(k\rightarrow0)=-a$
 
-Define $T$ matrix
-\eqar{
-  T\paren{\vec k', \vec k}=&U\paren{\vec k', \vec k}+\int\frac{\ud^3k''}{\paren{2\pi}^3}\frac{U\paren{\vec k', \vec k''}}{k^2/m-k''^2/m+\ui 0}T\paren{\vec k'', \vec k}\\
-  \Psi_s\paren{\vec k'}=&\frac{m}{k^2-k'^2+\ui 0}T\paren{\vec k', \vec k}\\
-  f\paren{\vec k', \vec k}=&-\frac{m}{4\pi\hbar^2}T\paren{\vec k', \vec k}
-}
+\subsection{Effective interaction}
+Althought the interaction potential between two atoms can be very strong and hard to calculate, they are usually very short range and the precise behavior can only affect the states with a large $k$.
+Therefore, for the state
 
-% Effective interaction
 % Energy cut-off \varepsilon_c

### 2015-05-14 term-paper/paper.tex
[term-paper] 2.3

@@
 \subsection{Effective interaction}
-Althought the interaction potential between two atoms can be very strong and hard to calculate, they are usually very short range and the precise behavior can only affect the states with a large $k$.
-Therefore, for the state
-
-% Energy cut-off \varepsilon_c
-% k_c, R
+Althought the interaction potential between two atoms can be very strong and hard to calculate, they are usually very short range and their precise behavior can only affect the states with a large $k$.
+Therefore, for the purpose of low energy collision in which both the initial and final state has a small $k$, it is useful to introduce a simple effective potential that can be used to describe these low energy process below a cut-off energy $\varepsilon_c$.
+Let the corresponding cut-off in wave vector and length be $k_c^2/m=\varepsilon_c$ and $R_c=k_c^{-1}$, we can write a effective potential $\tilde U\paren{\vec k', \vec k}$
+\[\tilde U\paren{\vec k', \vec k}=U\paren{\vec k', \vec k}+m\int_{k_c}\!\!\frac{\ud^3 k''}{\paren{2\pi}^3}\frac{U\paren{\vec k', \vec k''}}{k^2-k''^2+\ui 0}\tilde U\paren{\vec k'', \vec k}\]
+And express the scattering process using this potential and only low energy states as
+\[T\paren{\vec k', \vec k}=\tilde U\paren{\vec k', \vec k}+m\int^{k_c}\!\!\frac{\ud^3 k'}{\paren{2\pi}^3}\frac{\tilde U\paren{\vec k', \vec k''}}{k^2-k''^2+\ui0}T\paren{\vec k'', \vec k}\]
+The effective potential can now be any short range function that gives the correct scattering amplitude. As the simplest potential, the one that is usually taken is a $\delta$ function
+\[U\paren{\vec r}=U_0\delta^3\paren{\vec r}\]
+Using which we can write the equation for the scattering amplitude
 \eqar{
-  \tilde U\paren{\vec k', \vec k}=&U\paren{\vec k', \vec k}+\int_{k''^2/m>\varepsilon_c}\frac{\ud^3 k''}{\paren{2\pi}^3}\frac{\tilde U\paren{\vec k', \vec k''}}{k^2/m-k''^2/m+\ui 0}\tilde U\paren{\vec k'', \vec k}
+  f\paren{\vec k', \vec k}=&-\frac{mU\paren{\vec k'-\vec k}}{4\pi}\\
+  &+m\int^{k_c}\!\!\frac{\ud^3k''}{\paren{2\pi}^3}\frac{U\paren{\vec k'-\vec k''}f\paren{\vec k'',\vec k}}{k^2-k''^2+\ui0}
 }
+Since the major contribution of the integral comes from when $\abs{k}=\abs{k''}$, we can replace $f\paren{\vec k'', \vec k}$ by $f\paren{k}$ therefore
 \eqar{
-  T\paren{\vec k', \vec k}=&\tilde U\paren{\vec k', \vec k}+\int_{k''^2/m<\varepsilon_c}\frac{\ud^3 k'}{\paren{2\pi}^3}\frac{\tilde U\paren{\vec k', \vec k''}}{k^2/m-k''^2/m+\ui0}T\paren{\vec k'', \vec k}
+  \frac{1}{f\paren{k}}=&-\frac{4\pi}{mU_0}+4\pi\int^{k_c}\frac{\ud^3k''}{\paren{2\pi}^3}\frac{1}{k^2-k''^2+\ui0}\\
+  =&-\frac{4\pi}{mU_0}+\frac{2}{\pi}\paren{-k_c-\frac{k}{2}\ln\paren{-\frac{k_c-k-\ui0}{k_c+k+\ui0}}}\\
+  \approx&-\frac{4\pi}{mU_0}+\frac{2}{\pi}\paren{-k_c-\frac{\ui\pi k}{2}+\frac{k^2}{k_c}}
 }
-% U\paren{\vec r}=U_0\delta^3\paren{\vec r}
-% Energy conservation
-% mainly k' == k
-\eqar{
-  \frac{1}{f\paren{k}}=&-\frac{4\pi}{mU_0}+4\pi\int_{\abs{q}<1/R}\frac{\ud^3q}{\paren{2\pi}^3}\frac{1}{k^2-q^2+\ui0}\\
-  =&\frac{1}{2\pi^2}\paren{-\frac{1}{R}-\frac{k}{2}\ln\paren{-\frac{R^{-1}-k-\ui0}{R^{-1}+k+\ui0}}}\\
-  \approx&\frac{1}{2\pi^2}\paren{-\frac{1}{R}-\frac{\ui\pi k}{2}+k^2R}
-}
-
-% f\paren{0}=-a
-\eqar{
-  a=&\frac{\pi}{2}\frac{R}{1+\frac{2\pi^2R}{mU_0}}\\
-  f\paren{k}=&\frac{1}{a^{-1}+r_{eff}k^2/2-\ui k}
-}
-% Dependency of U_0 on R
+therefore
+\[a=&\frac{\pi}{2}\frac{mU_0}{mU_0k_c+2\pi^2}\]
+Note that non of the cut-off $k_c$ or the effective potential $U_0$ is physical but the scattering length $a$ is.
+Any physical process calculated with the effective model should only depend on physical quantities and $k_c$ and $U_0$ should drop out.
 

### 2015-05-14 term-paper/paper.tex
[term-paper] tweak

@@
 
-\section{Feshbach Resonance}
 % Cite optical feshbach resonance
-Feshbach resonance is a way to tune the interaction between two atoms.
+% Feshbach resonance is a way to tune the interaction between two atoms.
 It appears as a divergence in the scattering length when the energy of a molecular bound state matches or is closed to the energy of the free atom state.
@@
 
-In this section, we will describe a formal way to calculate the properties of $S$-wave scattering at low temperature.
-We will then apply this framework to a simplified model of Feshbach resonance consists of a open channel for the free atomic state and a closed channel for the molecular bound state.
+\section{Scattering theory}
+In this section, we will describe a formal way to calculate the properties of $S$-wave scattering between two atoms at low temperature.
 
@@
 \subsection{$T$-Matrix}
-The $T$-matrix is defined as a map from the initial state of the scattering (which is a $\delta$ function in $k$ space in our case) to the final state. It is defined as
-\eqar{
-  T\paren{\vec k', \vec k}=&U\paren{\vec k', \vec k}+m\int\frac{\ud^3k''}{\paren{2\pi}^3}\frac{U\paren{\vec k', \vec k''}}{k^2-k''^2+\ui 0}T\paren{\vec k'', \vec k}}
+The $T$-matrix is defined as a map from the initial state of the scattering (which is a $\delta$ function in $k$ space in our case) to the final state. It is defined as,
+\[\hat T=\hat V+\hat V\frac{1}{E-\hat H_0+\ui 0}\hat T\]
+For the scattering process in free space, the equation above can be represented in $k$ space as,
+\[T\paren{\vec k', \vec k}=U\paren{\vec k', \vec k}+m\int\frac{\ud^3k''}{\paren{2\pi}^3}\frac{U\paren{\vec k', \vec k''}}{k^2-k''^2+\ui 0}T\paren{\vec k'', \vec k}\]
 where the $+\ui 0$ denotes a infinitesimal quantity to ensure that we have outgoing waves.
@@
 therefore
-\[a=&\frac{\pi}{2}\frac{mU_0}{mU_0k_c+2\pi^2}\]
+\[a=\frac{\pi}{2}\frac{mU_0}{mU_0k_c+2\pi^2}\]
 Note that non of the cut-off $k_c$ or the effective potential $U_0$ is physical but the scattering length $a$ is.

### 2015-05-14 term-paper/paper.tex
[term-paper] 3.1

@@
 
-\subsection{Multichannel scattering and Feshbach resonance}
-% Hamiltonian
+\section{Confinement induced resonance}
+When atoms are confined in a strong trapping potential in certain directions but not in the others, their motion in the confined directions can be completely frozen out if the chemical potential of each partical is much smaller than the excitation energy of the trap.
+On the other hand, in the other directions, there is no trapping potentials and the motion of the atoms are effectively the same with that of atoms in a lower dimension.
+When considering the collisional properties in such a geometry, one might naively expect that the confinement does not contribute much because of the difference in energy scales.
+This assumption is usually true but can break down near a Feshbach resonance.
+Due to the strong interaction between the atoms, high vibrational state in the confined direction can be virtually excited during a collision and therefore modify the properties of the collision.\\
+
+The right way to study the process is to do a three dimensional calculation of the collision which include all the transversely excited states.
+In this section, we will use the framework we have developed above to calculate the collisional properties in a strong harmonic transverse potential.
+In order to normalize the result at the cut-off energy scale, we compare our result to the well-known free-space Feshbach resonance.
+
+\section{Separation of motion}
+The advantage of using harmonic confinement is that center-of-mass (COM) motion and the relative motion can be separated. Given the Hamiltonian of two interacting particles
 \eqar{
-  \hat H_0|\vec k\rangle=&
+  H=&\frac{1}{2m}\sum_{i;\alpha}p_{i\alpha}^2+\frac{m\omega^2}{2}\sum_{i;\alpha<d_\perp}x_{i\alpha}^2+V
 }
-% Solution
-
-% Bound states
-
-% Compare to generic fomula and get scattering length
-
-\section{Confinement induced resonance}
-% Seperate COM and relative
+where $i=1,2$ is the index of particles, $\alpha$ is the index of dimensions, $d_\perp$ is the number of confined dimensions and $V=V\paren{\vec r_1, \vec r_2}$ is the interaction potential.
+If we define center-of-mass coordinates
+\eqar{
+  X_\alpha=&\frac{x_{1\alpha}+x_{2\alpha}}{2}&P_\alpha=&p_{1\alpha}+p_{2\alpha}
+}
+and relative coordinates
+\eqar{
+  x_\alpha=&x_{1\alpha}-x_{2\alpha}&p_\alpha=&\frac{p_{1\alpha}-p_{2\alpha}}{2}
+}
+the new coordinates still satisfies the canonical commutation relation and the Hamiltonian is fully separated
+\eqar{
+  H=&H_{CM}+H_{rel}\\
+  H_{CM}=&\frac{1}{4m}\sum_\alpha P_\alpha^2+m\omega^2\sum_\alpha X_\alpha^2\\
+  H_{rel}=&\frac{1}{m}\sum_\alpha p_\alpha^2+\frac{m\omega^2}{4}\sum_\alpha x_\alpha^2+V\paren{\vec r_{12}}
+}
+And the relative motion problem, therefore the collision problem, is reduced to a single partical problem.
 

### 2015-05-15 term-paper/paper.tex
[term-paper] 3.2

@@
 For the scattering process in free space, the equation above can be represented in $k$ space as,
-\[T\paren{\vec k', \vec k}=U\paren{\vec k', \vec k}+m\int\frac{\ud^3k''}{\paren{2\pi}^3}\frac{U\paren{\vec k', \vec k''}}{k^2-k''^2+\ui 0}T\paren{\vec k'', \vec k}\]
+\[T\paren{\vec k', \vec k, E}=U\paren{\vec k', \vec k}+\int\frac{\ud^3k''}{\paren{2\pi}^3}\frac{U\paren{\vec k', \vec k''}}{E-k''^2/m+\ui 0}T\paren{\vec k'', \vec k, E}\]
 where the $+\ui 0$ denotes a infinitesimal quantity to ensure that we have outgoing waves.
@@
 Using the $T$-matrix, we can express the scattered wavefunction as
-\[\Psi_s\paren{\vec k'}=\frac{m}{k^2-k'^2+\ui 0}T\paren{\vec k', \vec k}\]
+\[\Psi_s\paren{\vec k'}=\frac{m}{k^2-k'^2+\ui 0}T\paren{\vec k', \vec k, \frac{k^2}m}\]
 And we cans also define the scattering amplitude as
-% \[f\paren{\vec k', \vec k}=-\frac{m}{4\pi\hbar^2}T\paren{\vec k', \vec k}\]
-\[f\paren{\vec k', \vec k}=-\frac{m}{4\pi}T\paren{\vec k', \vec k}\]
+\[f\paren{\vec k', \vec k}=-\frac{m}{4\pi}T\paren{\vec k', \vec k, \frac{k^2}{m}}\]
 For the problem we are considering, we will take the limit of $k, k'\rightarrow0$, therefore
-\[\Psi_s\paren{\vec k'}=\frac{m}{k^2-k'^2+\ui 0}T\paren{0, 0}\]
+\[\Psi_s\paren{\vec k'}=\frac{m}{k^2-k'^2+\ui 0}T\paren{0, 0, 0}\]
 In real space
 \eqar{
-  \Psi_s\paren{\vec r}=&\int\frac{\ud k'^3}{\paren{2\pi}^3}\frac{m\ue^{\ui\vec k'\cdot\vec r}}{k^2-k'^2+\ui 0}T\paren{0, 0}\\
-  =&-\frac{m\ue^{\ui kr}}{4\pi r}T\paren{0, 0}
+  \Psi_s\paren{\vec r}=&\int\frac{\ud k'^3}{\paren{2\pi}^3}\frac{m\ue^{\ui\vec k'\cdot\vec r}}{k^2-k'^2+\ui 0}T\paren{0, 0, 0}\\
+  =&-\frac{m\ue^{\ui kr}}{4\pi r}T\paren{0, 0, 0}
 }
@@
 And express the scattering process using this potential and only low energy states as
-\[T\paren{\vec k', \vec k}=\tilde U\paren{\vec k', \vec k}+m\int^{k_c}\!\!\frac{\ud^3 k'}{\paren{2\pi}^3}\frac{\tilde U\paren{\vec k', \vec k''}}{k^2-k''^2+\ui0}T\paren{\vec k'', \vec k}\]
+\eqar{
+  T\paren{\vec k', \vec k, E}=&\tilde U\paren{\vec k', \vec k}\\
+  &+\int^{k_c}\!\!\frac{\ud^3 k'}{\paren{2\pi}^3}\frac{\tilde U\paren{\vec k', \vec k''}}{E-k''^2/m+\ui0}T\paren{\vec k'', \vec k, E}
+}
 The effective potential can now be any short range function that gives the correct scattering amplitude. As the simplest potential, the one that is usually taken is a $\delta$ function
@@
 
-\section{Separation of motion}
+\subsection{Separation of motion}
 The advantage of using harmonic confinement is that center-of-mass (COM) motion and the relative motion can be separated. Given the Hamiltonian of two interacting particles
 \eqar{
-  H=&\frac{1}{2m}\sum_{i;\alpha}p_{i\alpha}^2+\frac{m\omega^2}{2}\sum_{i;\alpha<d_\perp}x_{i\alpha}^2+V
+  H=&\frac{1}{2m}\sum_{i;\alpha}p_{i\alpha}^2+\frac{m\omega^2}{2}\sum_{i;\alpha<d_\perp}x_{i\alpha}^2+U
 }
-where $i=1,2$ is the index of particles, $\alpha$ is the index of dimensions, $d_\perp$ is the number of confined dimensions and $V=V\paren{\vec r_1, \vec r_2}$ is the interaction potential.
+where $i=1,2$ is the index of particles, $\alpha$ is the index of dimensions, $d_\perp$ is the number of confined dimensions and $U=U\paren{\vec r_1, \vec r_2}$ is the interaction potential.
 If we define center-of-mass coordinates
@@
   H_{CM}=&\frac{1}{4m}\sum_\alpha P_\alpha^2+m\omega^2\sum_\alpha X_\alpha^2\\
-  H_{rel}=&\frac{1}{m}\sum_\alpha p_\alpha^2+\frac{m\omega^2}{4}\sum_\alpha x_\alpha^2+V\paren{\vec r_{12}}
+  H_{rel}=&\frac{1}{m}\sum_\alpha p_\alpha^2+\frac{m\omega^2}{4}\sum_\alpha x_\alpha^2+U\paren{\vec r_{12}}
 }
@@
 
-% Cutoff
+\subsection{Calculation of the $T$-matrix}
+Instead of the $k$ bases we used for the free-space problem, it is convinient to use the eigen-functions of the non-interacting Hamiltonian as our basis.
+\eqar{
+  \phi=&\prod_{\beta<d_\perp}\phi_n\paren{x_\beta}\prod_{\alpha\geqslant d_\perp}\ue^{\ui k_\alpha}
+}
+Since we assume only the lowest transverse vibrational state is populated, the quantity we need to calculate is
+\[T_{0,0}=\langle0|\hat T|0\rangle\]
+where $|0\rangle$ is the ground state of the non-interacting system. Using $\langle r|U|r'\rangle=U_0\delta\paren{r}\delta\paren{r'}$ we have
+\eqar{
+  T_{0,0}=&U_0+U_0T_0\langle0|\frac{1}{E-H_0+\ui0}|0\rangle\\
+  T_{0,0}^{-1}=&U_0^{-1}-\int_0^\infty\langle0|\ue^{\paren{E-H_0+\ui0}\tau}|0\rangle\ud\tau\\
+  =&U_0^{-1}\\
+  &-\int_0^\infty\ue^{\paren{E+\ui0}\tau}\paren{\frac{m\omega}{4\pi\sinh\omega\tau}}^{d_\perp/2}\paren{\frac{m}{4\pi\tau}}^{\paren{3-d_\perp}/2}\ud\tau
+}
+Instead of choosing a cut-off energy scale in order to calculate the integral we can compare this expression to the result without confinement.
+Since we know that in the free space $d_\perp=0$ and when $E=0$,
+\eqar{
+  \frac{m}{4\pi a}=&U_0^{-1}-\int_0^\infty\paren{\frac{m}{4\pi\tau}}^{3/2}\ud\tau
+}
+where $a$ is the three dimensional scattering length we replaced the $U_0$ that needs a cut-off with the integral above and the expression for the $T$-matrix is
+\eqar{
+  T_{0,0}^{-1}=&\frac{m}{4\pi a}\\
+  &+\int_{0}^{\infty}\lparen{\paren{\frac{m\omega}{4\pi\sinh\omega\tau}}^{d_\perp/2}\paren{\frac{m}{4\pi\tau}}^{\paren{3-d_\perp}/2}}\\
+  &\rparen{-\paren{\frac{m}{4\pi\tau}}^{3/2}}\ue^{\paren{E+\ui0}\tau}\ud\tau
+}
 
-% Compare to 3-d
-
-% Bound state
-
-% Scattering length
+\subsection{Bound state in one dimension}
 

### 2015-05-15 term-paper/paper.tex
[term-paper] 3.3

@@
 \subsection{Bound state in one dimension}
+In the case of a one dimentional system, $d_\perp=2$.
+Let $\varepsilon=\dfrac{E}{\omega}-1$, which is the energy of the system above the zero point energy of the confinement.
+For low energy state (i.e.
+$\abs{\varepsilon}\ll1$)
+\eqar{
+  T^{-1}\approx&\frac{m}{4\pi a}+\frac{m}{4\pi}\sqrt{\frac{m\omega}{2}}\paren{\sqrt{\frac{2}{-\varepsilon}}+O\paren{1}}
+}
+The pole of the $T$-matrix gives the energy of the bound state and we can see that the energy for the bound states is given by
+\eqar{
+  \varepsilon=-m\omega^2a^2
+}
+Compare to the case of a free space Feshbach resonance which only have bound states for a positive scattering length, a bound state exist even for negetive scattering length when the system is confined in one dimension.
 

### 2015-05-15 term-paper/paper.tex
[term-paper] intro

@@
 \tikzstyle{every picture}+=[remember picture]
-\title{Confinement induced resonance}
+\title{Feshbach resonance in confined geometry}
 \author{Yichao Yu}
@@
 \begin{abstract}
-  We present a formal derivation of the confinement induced resonance for particles in a lower dimension.
+  We present a formal derivation of the Feshbach resonance for particles in a lower dimension.
 The generic $T$-matrix method is used to calculate the $S$-wave collisional property between two ultra-code atoms.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
-In the field of ultra-cold atoms and molecules, the collisional properties between the particles play an important role for cooling into quantum degeneracy.
-The tunability of the scattering length using Feshbach resonance opens the door for engineering the interaction and using it as a source of correlation and entanglement in a many-body system.
+\section*{Introduction}
+In the field of ultra-cold atoms and molecules, the collisional properties between the particles play an important role, e.g.
+for cooling into quantum degeneracy.
+The strengh of this interaction, the scattering length, can be tuned in the experiment using Feshbach resonance, which appears as a divergence in the scattering length when the energy of a molecular bound state is tuned to match or closed to the energy of the free atom state.
+This easy tunability of the interaction between particles opens the door for engineering the interaction and using it as a source of correlation and entanglement in a many-body system.
+The bound state that appears on one side of the Feshbach resonance have also been used to create ultra-cold molecules from ultra-cold atoms.\\
 
-% Cite optical feshbach resonance
-% Feshbach resonance is a way to tune the interaction between two atoms.
-It appears as a divergence in the scattering length when the energy of a molecular bound state matches or is closed to the energy of the free atom state.
-The relative energy between the molecular and atomic is usually tuned using the magnetic field and the difference in Zeeman effect between the two states although optical dressing has also been used on excited metastable state.\\
+Another interesting topic for ultra-cold physics is lower dimensional systems.
+The dynamics in these systems have many features that are very different from the ones in three dimention.
+Such a system can be created in the experiment by loading ultra-cold atoms into a strong confinement such that only the lowest excited state in the trap can be populated.
+While the dynamics in a confined system is usually not sensitive to the higher excited states, this approximation breaks down in the present of the Feshbach resonance in which the interaction energy can be sufficiently large to populate those states.\\
+
+In this review, we will present a formal way to handle this problem.
+We will first study the generic $S$-wave scattering problem and derive the generic expression for the scattering length.
+In the second section, we will apply this method to the lower dimensional problem and use it to derive the energy of bound states with the present of external confinement in a one dimensional system.
 

### 2015-05-15 term-paper/paper.tex
[term-paper] conclud

@@
 This easy tunability of the interaction between particles opens the door for engineering the interaction and using it as a source of correlation and entanglement in a many-body system.
-The bound state that appears on one side of the Feshbach resonance have also been used to create ultra-cold molecules from ultra-cold atoms.\\
+The bound state that appears on one side of the Feshbach resonance have also been used to create ultra-cold molecules from ultra-cold atoms.\cite{jila-krb}\\
 
@@
 We will first study the generic $S$-wave scattering problem and derive the generic expression for the scattering length.
-In the second section, we will apply this method to the lower dimensional problem and use it to derive the energy of bound states with the present of external confinement in a one dimensional system.
+In the second section, we will apply this method to the lower dimensional problem and use it to derive the energy of bound states with the present of external confinement in a one dimensional system\cite{feshbach-lecture-note}.
 
@@
 \section{Conclusion}
+We have shown that the low energy $S$-wave scattering can be described by a single parameter, the scattering length $a$.
+Due to the strong interaction energy caused by a Feshbach resonance, the interaction can be modified by higher vibrational excitations of the trap.
+As an example, we have shown that there are additional bound state in the present of the confinement.
 
